---
title: "claut"
output: github_document
bibliography: inst/REFERENCES.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Functions from the University of Toronto Climate Lab

This package, currently at a very early stage of development, will eventually host many of the functions generated at the University of Toronto Climate Lab. For now, I (Conor Anderson) am the sole maintainer of, and contributor to, this package, however, I hope that eventually all of the miscellaneous functions that are produced in the lab can find their way into this package. Any function contained in this package is documented. Type `?function_name` in R to access this documentation. I consider this to be a "working package"; the functions contained herein are likely to change and/or may be split away into other projects without warning. 

## Installation

This package can be installed via the `install_git()` function in the `devtools` or `remotes` packages, or by running the following convenience script.

``` {r, eval = FALSE}
source("https://gitlab.com/ConorIA/claut/raw/master/install_claut.R")
```

## Functions used in published papers

  - [`deltaDTD()`](https://gitlab.com/ConorIA/claut/blob/master/R/deltaDTD.R): Calculate a number of measures of diurnal temperature variability [@anderson_2018_characterization]
  - [`missing_value_lab()`](https://gitlab.com/ConorIA/claut/blob/master/R/missing_value_lab.R): A function to artificially introduce missing values into a year&ndash;month of data, replace those missing values with linear interpolation and cubic splines, and then calculate the error in the calculated mean. [@anderson_2018_accounting] 

## Functions used in papers in review

The following functions were used in studies that are currently under review. If you are a reviewer, this is probably what you are looking for. Note that these functions may undergo some minor optimization or code changes, but the results that they produce will always be the same. 

  - [`subensembles()`](https://gitlab.com/ConorIA/claut/blob/master/R/missing_value_lab.R): Takes a table of GCM anomalies generated by the [_Conjuntool_](https://gitlab.com/ConorIA/conjuntool) and provides optimal sub-ensembles based on the ability of a sub-ensemble of size $k$ to reproduce an observed baseline.

## Functions implementing other published work
  - [`solar_daily()`](https://gitlab.com/ConorIA/claut/blob/master/R/solar_daily.R): Calculates daily maxima and minima after @zaknic-catovic_2018_comparison.

## Misc functions

There are some other helper functions in this package that are here in hopes that they prove useful to someone someday. These are: 

  - [`describe_snaps()`](https://gitlab.com/ConorIA/claut/blob/master/R/describe_snaps.R): Describes the lengths or other characteristics of run-length-encoded events, such as cold snaps or heatwaves.
  - [`suntimes()`](https://gitlab.com/ConorIA/claut/blob/master/R/suntimes.R): Calculates sunrise, solar noon, and sunset times for a given location and date.
  - [`trim_data()`](https://gitlab.com/ConorIA/claut/blob/master/R/trimData.R): An easy function to trim a `data.frame` to given start and end years
  - functions for working with ASCII gridded data; these were originally written to parse NOAA's [GHCN Merged gridded data set](https://www.ncdc.noaa.gov/temp-and-precip/ghcn-gridded-products/)
    - [`parse_ASCII_grid()`](https://gitlab.com/ConorIA/claut/blob/master/R/parse_ASCII_grid.R): Reads an ASCII file of gridded data into a 3D matrix. This is currently quite slow and a little noisy, but it works.
    - [`generate_wkt_csv()`](https://gitlab.com/ConorIA/claut/blob/master/R/generate_wkt_csv.R): This function takes a list of matrix names and generates a `.csv` file of WKT-formatted polygons for import into QGIS and other GIS software.

## Other resources

Some of the functions that _were_ contained in the package have been moved to my [_Conjuntool_ project](https://gitlab.com/ConorIA/conjuntool).
For other resources from the climate lab and beyond, please see our [CL@UT Resources List](https://gitlab.com/ConorIA/claut-resources).

## Contributing to the `claut` package

The members of the Climate Lab are, first and foremost, academics and researchers, not coders. If you would like to contribute code improvements or patches to any of the functions here, please feel free to open a [merge request](https://gitlab.com/ConorIA/claut/merge_requests). Please note that code you contribute will be attributed to you, and will be released under the terms of the [GNU GPLv3](https://gitlab.com/ConorIA/claut/blob/master/LICENSE.md).
<br>

## References
